Containers and R---the Rockerverse and beyond

### 2020-01-13 manuscript.Rmd

- `RSelenium`
- [`googleComputeEngineR`](https://cloudyr.github.io/googleComputeEngineR/) (function `docker_run`)
  - I don't think `docker_run` is main focus for containers for this package, its more how it uses Docker to launch custom environments that can be templated (e.g., rstudio, shiny etc.) and for parrallisation e.g., `library(future)`  using GCE VMs as endpoints. [@MarkEdmondson1234]
- [`analogsea`](https://github.com/sckott/analogsea) (digital ocean R client)
- [`AzureContainers`](https://cran.r-project.org/package=AzureContainers): Umbrella package for working with containers in Microsoft's Azure cloud. Provides interfaces to three Azure services: Container Registry, Container Instances (for running individual containers), and Kubernetes Services (for orchestrated deployments)

@@

- [dynwrap](https://github.com/dynverse/dynwrap_containers/blob/master/.travis.yml) [@rcannood]
  - For this project, we use travis-ci to build rocker-derived containers, test them, and only push them to docker hub (from travis-ci.org) if the integration tests succeed.
- Google Cloud Build [@MarkEdmondson1234]
  - https://cloud.google.com/cloud-build/
  - For me this is what makes Docker containers viable, as it builds the `Dockerfile`s on each GitHub commit.  It couples with Google Container Registry to build private Docker images, for downstream applications.

@@

- Docker images for cloud services [@MarkEdmondson1234]
  - the most popular functionality for `googleComputeEngineR` is its use of Docker to enable parallel processing across VMS - [some demos here](https://cloudyr.github.io/googleComputeEngineR/articles/massive-parallel.html)
- Google Cloud Run - CaaS (Containers as a Service) that lets you launch a Docker container without worrying about underlying infrastructure. An R implementation is shown here at [cloudRunR](https://github.com/MarkEdmondson1234/cloudRunR) which uses it to create a scalable R plumber API. 
- `batchtools` \citep{Lang2017batchtools} can [schedule jobs with Docker Swarm](https://mllg.github.io/batchtools/reference/makeClusterFunctionsDocker.html)
- scalable deployments, e.g., start with numerous Shiny talks mentioning Rocker at useR!2017
- [dynmethods](https://github.com/dynverse/dynmethods) [@rcannood]: In order to evaluate ±50 computational methods which all used different environments (R, Python, C++, ...), we wrapped each of them in a docker container and can execute these methods from R. Again, all of these containers are being built on travis-ci, and will only be pushed to docker hub if the integration test succeeds.

>>>>

- `RSelenium`
- [`googleComputeEngineR`](https://cloudyr.github.io/googleComputeEngineR/) (function `gce_vm_template()`)
  - To enable quick deployments of key R services such as RStudio and Shiny onto cloud virtual machines (VMs), this package utilises Dockerfiles to move the labour of setting up those services from the user to a premade Docker image.  For example, by specifying the template `template="rstudio"` in `gce_vm_template()/gce_vm()` an up to date RStudio Service image is launched.  Specifying `template="rstudio-gpu"` will launch an RStudio Server image with a GPU attached, etc.  
- [`analogsea`](https://github.com/sckott/analogsea) (digital ocean R client)
- [`plumber`](https://www.rplumber.io/docs/hosting.html#docker)
- [production deployment of neural networks](https://github.com/tmobile/r-tensorflow-api) [@jnolis, @nolistic]
- Kubernetes - A popular platform for managing Docker containers is [Kubernetes](https://kubernetes.io/), which is used for a wide variety of containerized applications.  It may be your organisation has a Kubernetes cluster already for other applications.  Docker containers are used within Kubernetes clusters to hold native code, for which Kubernetes creates a framework around network connections and scaling of resources up and down.  An introduction on using [Kubernetes with R is published at this blog post](https://code.markedmondson.me/r-on-kubernetes-serverless-shiny-r-apis-and-scheduled-scripts/).
- [`AzureContainers`](https://cran.r-project.org/package=AzureContainers): Umbrella package for working with containers in Microsoft's Azure cloud. Provides interfaces to three Azure services: Container Registry, Container Instances (for running individual containers), and Kubernetes Services (for orchestrated deployments)

@@

- [dynwrap](https://github.com/dynverse/dynwrap_containers/blob/master/.travis.yml) [@rcannood]
  - For this project, we use travis-ci to build rocker-derived containers, test them, and only push them to docker hub (from travis-ci.org) if the integration tests succeed.
- Google Cloud Build
  - https://cloud.google.com/cloud-build/
  - Cloud Build is another continuous intergation service that helps move the workload of building the Docker images to an online service.  Cloud Build can be set up to build the Dockerfiles on each GitHub commit or release.  This means you do not need to build the Docker images locally, which can tie up resources since Docker images can be several GBs and take a long time to compile. Google Cloud Build works alongside Google Container Registry to allow you to build private and public Docker images, which allows you to build up your own dependency graphs for downstream applications.

@@

- Docker images for cloud services
  - A popular application of using Docker is to create the environments that can run in parallel for speeding up R code.  For example, [`googleComputeEngineR`](https://CRAN.R-project.org/package=googleComputeEngineR)'s `gce_vm_cluster()` function can create clusters of 2 or more virtual machines, running multi-CPU architectures.  Instead of running a local R script with the local CPU and RAM restrictions, the same code can be processed on all CPU threads of the cluster of machines in the cloud, all running in a Docker container with the same R environments.   This is achieved through `googleComputeEngineR`'s integration with the R parralisation library [`library(future)` by Henrik Bengtsson]( https://CRAN.R-project.org/package=future).  Local R computation can be thrown up to a multi-CPU and VM environment to achieve parrell computation in a few lines of R code in your local session. - [some demonstrations are available here](https://cloudyr.github.io/googleComputeEngineR/articles/massive-parallel.html). 
- [Google Cloud Run](https://cloud.run) - This is a CaaS (Containers as a Service) that lets you launch a Docker container without worrying about underlying infrastructure.  This dispenses with the developer creating a cloud server to run the Docker image on, by abstracting away those servers to a more serverless configuration.  Cloud Run lets you run your code on top of a managed or your own Kubernetes cluster running Knative, and can accept any Docker image.  The service takes care of network ingress, scaling machines up and down to zero, authentication and authorisation, all features which are non-trivial for a developer to create on their own.  This can be used to scale up R code to millions of instances if they need to, with little or no changes to existing code. An R implementation is shown here at [cloudRunR](https://github.com/MarkEdmondson1234/cloudRunR) which uses Cloud Run to create a scalable R plumber API. 
- `batchtools` \citep{Lang2017batchtools} can [schedule jobs with Docker Swarm](https://mllg.github.io/batchtools/reference/makeClusterFunctionsDocker.html)
- scalable deployments, e.g., start with numerous Shiny talks mentioning Rocker at useR!2017
- [dynmethods](https://github.com/dynverse/dynmethods) [@rcannood]: In order to evaluate ±50 computational methods which all used different environments (R, Python, C++, ...), we wrapped each of them in a docker container and can execute these methods from R. Again, all of these containers are being built on travis-ci, and will only be pushed to docker hub if the integration test succeeds.
